---
title: 'Project 1: A C4.5 analysis of a Wine Quality Dataset.'
author: "Þórgnýr Thoroddsen & Anna Margrét Björnsdóttir"
date: "9/12/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FSelector)
```


###Data Wrangling
We start by importing the data and looking at the attributes it contains.

```{r}
data <- read.table("data/winequality-red.csv", header = TRUE, sep = ";", dec = ".")
str(data)
```

When we check the dataset we see that all of the attributes are numerical with good reason. We'll be making a C4.5 decision tree to try and predict how the wines get classified in terms of quality. Let's view the quality attribute a little closer.

```{r}
hist(data$quality)
levels(as.factor(data$quality))
```

The objective is to classify the items in the dataset correctly. More importantly, since we're all lovers of great wines, we'll make it a priority to classify the high quality wines over the other ones. Furthermore, simple decision trees are clearly optimal.

But first let's peer a bit into the dataset:  
* There's no missing data so we luckily don't have to deal with that.  
* The outliers in the data do not seem to be significant. They need not be dealt with.  

###Creating the C4.5 tree.

As we started fiddling with treemaking in Weka we quickly realized that a tree model would never fulfill our dreams of finding the magic behind the perfect wine. We, however, figured we'd try to optimize the tree in such as a way to maximize the predicit






####STRUCTURE
Skoða gögn. Ræða outliers og etc.

Skiptum í þrennt
-Keyra default
-Optimize'a fyrir smæð
-Optimize'a fyrir HIGH

Skiptum í tvennt
-keyra default
-Optimize'a fyrir smæð
-Optimize'a fyrir HIGH







